### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Bilb - Added 5 Deconvolution sources and check their compiling
Results - XRD - moved reference notes from intro into the XRD section.

Key sources \cite{Zhang2013, Zhang2012} 
\cite{Zhang2011}

@@

Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined. This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original \acrshort{dsc} \glspl{ht} for both the bulk and film, see Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}. Similar solutions to \acrshort{dsc} deconvolution \cite{

The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are not obtained from the deconvolution.

@@

>>>>

@@

Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined. This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}. The details of the fits for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.

The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are not obtained from the original raw data, not the deconvolution.

@@

Note: Key XRD sources for \MgZnCa crystallisation phase identification \cite{Zhang2013, Zhang2012, Zhang2011}
